SPIDERMAN

### 2016-09-14 ms.tex
added lots of plots

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/b53.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

@@

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_quad.pdf}
\caption{This is a caption}
\label{fig:zhang_quad}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_quad_bright.pdf}
\caption{Same as \ref{fig:zhang_quad}, but the scale is now flux instead of temperature. A blackbody spectrum and a channel of 1.1-1.7 microns was assumed to make the conversion. The option exists to add limb darkening to this profile.}
\label{fig:zhang_quad2}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

@@

\subsection{Integrator validation}\label{sec:numerical}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/precision.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

\subsection{Performance}\label{sec:performance}

In typical usage, SPIDERMAN is capable of producing over 1000 models per second on a single core. This means that a 1 million MCMC sample can be generated in approximately a quarter of an hour.

The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.

\subsection{Performance}\label{sec:performance}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/exec_time.pdf}
\caption{This is a caption}
\label{fig:exec_time}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/system.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}
